$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-02-27 paper/e6ssm-tuning-paper.tex
Added 2-loop beta function for y_t
Added simplified O(t^2) coefficient for y_t
Added in missing factor of 1/2
Added one-loop beta function for mq222
Added one-loop beta function for mu222
Fixed typo
Fixed some more typos
Added one-loop beta function for A_t
Rewrote one-loop beta for TYu22 in a form that makes the beta function for A_t easier to extract
Rewrote one-loop beta for TLambdax to make getting beta function for A_\lambda easier; there still appears to be a problem with the 2-loop beta for A_t (and maybe A_\lambda?), with disagreement between the CE6SSM results and the SARAH results
Ad

$U(1)$ and $E_6$ inspired extensions of the MSSM have been studied
very widely in the literature \cite{Gunion:1989we, Gunion:1992hs,
  Binetruy:1985xm, Ellis:1986yg, Ibanez:1986si, Gunion:1986ky,
  Haber:1986gz, Baer:1987eb, Gunion:1987jd, Grifols:1986vr,
  Ellis:1986ip, Morris:1987fm, Drees:1987tp, Ma:1995xk,
  Suematsu:1997tv, Suematsu:1997qt, Suematsu:1997au, Keith:1996fv,
  Keith:1997zb, Gherghetta:1996yr, Demir:1998dk, Langacker:1998tc,
  Hambye:2000bn, Ma:2000jf} (or for reviews see
\cite{Hewett:1988xc,Langacker:2008yv}).  There has also been a lot of
work recently including investigations of the neutralino sector
\cite{Hesselbach:2001ri, Barger:2005hb, Choi:2006fz,
  Barger:2007nv}; the relic abundance of dark matter
\cite{Kalinowski:2008iq}; GUT scale family symmetries which can
explain the hierarchy of masses in the fermion sector and their
associated mixings \cite{Stech:2008wd}; neutrino physics
\cite{Kang:2004ix}; explanations of the matter-anti-matter asymmetry
of the universe though EW baryogensis or leptogensis
\cite{Hambye:2000bn,Ma:2000jf,Kang:2004pp}; dipole moments
\cite{GutierrezRodriguez:2006hb}; anomaly mediated SUSY breaking with
D-term contributions \cite{Asano:2008ju} and the (extended) Higgs
sectors \cite{Daikoku:2000ep,Ham:2008xf}.

@@

\beta_{a_\lambda}^{(1)}&=2\lambda \left [ 2 \Sigma_{a_\lambda}+3\Sigma_{a_\kappa}+3y_ta_t+3y_ba_b+y_\tau a_\tau+\frac{3}{5}g_1^2M_1+3g_2^2 M_2+2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\right ]\nonumber\\
&{}+a_\lambda \left [ 6\lambda^2+2\Sigma_\lambda+3\Sigma_\kappa+3y_t^2+3y_b^2+y_\tau^2-\frac{3}{5}g_1^2-3g_2^2-2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\

@@

Note that $a_{\lambda_i}\equiv\lambda_i A_{\lambda_i}$, $a_{\kappa_i}\equiv\kappa_i A_{\kappa_i}$, $a_t\equiv y_t A_t$, $a_b\equiv y_b A_b$ and $a_\tau= y_\tau A_\tau$. Definining 

@@

\beta_{y_t}^{(2)}&=,\label{eq:USSMYu22BetaTwoLoop}\\
b_{y_t}^{(2)}&=,\label{eq:USSMYu22Ot2Coeff}

@@

\beta_{a_t}^{(1)}&=,\label{eq:USSMTYu22BetaOneLoop}\\

@@

\beta_{m_{Q3}^2}^{(1)}&=,\label{eq:USSMmq222BetaOneLoop}\\

@@

\beta_{m_{u3}^2}^{(1)}&=,\label{eq:USSMmu222BetaOneLoop}\\
\beta_{m_{u3}^2}^{(2)}&=,\label{eq:USSMmu222BetaTwoLoop}\\

>>>>

$U(1)$ and $E_6$ inspired extensions of the MSSM have been studied
very widely in the literature \cite{Gunion:1989we, Gunion:1992hs,
  Binetruy:1985xm, Ellis:1986yg, Ibanez:1986si, Gunion:1986ky,
  Haber:1986gz, Baer:1987eb, Gunion:1987jd, Grifols:1986vr,
  Ellis:1986ip, Morris:1987fm, Drees:1987tp, Ma:1995xk,
  Suematsu:1997tv, Suematsu:1997qt, Suematsu:1997au, Keith:1996fv,
  Keith:1997zb, Gherghetta:1996yr, Demir:1998dk, Langacker:1998tc,
  Hambye:2000bn, Ma:2000jf} (or for reviews see
\cite{Hewett:1988xc,Langacker:2008yv}).  There has also been a lot of
work recently including investigations of the neutralino sector
\cite{Hesselbach:2001ri, Barger:2005hb, Choi:2006fz,
  Barger:2007nv}; the relic abundance of dark matter
\cite{Kalinowski:2008iq}; GUT scale family symmetries which can
explain the hierarchy of masses in the fermion sector and their
associated mixings \cite{Stech:2008wd}; neutrino physics
\cite{Kang:2004ix}; explanations of the matter-anti-matter asymmetry
of the universe though EW baryogenesis or leptogenesis
\cite{Hambye:2000bn,Ma:2000jf,Kang:2004pp}; dipole moments
\cite{GutierrezRodriguez:2006hb}; anomaly mediated SUSY breaking with
D-term contributions \cite{Asano:2008ju} and the (extended) Higgs
sectors \cite{Daikoku:2000ep,Ham:2008xf}.

@@

\beta_{a_\lambda}^{(1)}&=a_\lambda \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( \tilde{Q}_1^2 + \tilde{Q}_2^2 + \tilde{Q}_S^2\right )g_1'^2 \right]\nonumber\\
&{}+\lambda \left [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\right.\nonumber\\
&{}\left.+4g_1'^2M_1'\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\

@@

Note that $a_{\lambda_i}\equiv\lambda_i A_{\lambda_i}$, $a_{\kappa_i}\equiv\kappa_i A_{\kappa_i}$, $a_t\equiv y_t A_t$, $a_b\equiv y_b A_b$ and $a_\tau= y_\tau A_\tau$. Defining 

@@

\beta_{y_t}^{(2)}&=y_t\bigg \{-22y_t^4-5y_b^4-5y_t^2y_b^2-y_b^2y_\tau^2-\lambda^2 \left ( \lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda + 3\Sigma_\kappa\right )\nonumber\\
&{}+2g_1'^2\left [ \lambda^2\left ( \tilde{Q}_1^2-\tilde{Q}_2^2+\tilde{Q}_S^2 \right )+2y_t^2\left ( 2\tilde{Q}_Q^2+\tilde{Q}_u^2\right )+y_b^2\left ( \tilde{Q}_1^2-\tilde{Q}_Q^2+\tilde{Q}_d^2\right )\right ]\nonumber\\
&{}+16g_3^2y_t^2+6g_2^2y_t^2+g_1^2\left ( \frac{6}{5}y_t^2+\frac{2}{5}y_b^2\right )+\frac{128}{9}g_3^4+\frac{33}{2}g_2^4+\frac{3913}{450}g_1^4\nonumber\\
&{}+2g_1'^4\left [ 2\left ( \tilde{Q}_2^4+\tilde{Q}_Q^4+\tilde{Q}_u^4\right )+\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2\right )\Sigma_{\tilde{Q}}\right ]+8g_3^2g_2^2+\frac{136}{45}g_3^2g_1^2\nonumber\\
&{}+\frac{32}{3}g_3^2g_1'^2\left ( \tilde{Q}_Q^2+\tilde{Q}_u^2\right )+g_2^2g_1^2+6g_2^2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2\right )\nonumber\\
&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3\tilde{Q}_2^2+\frac{1}{3}\tilde{Q}_Q^2+\frac{16}{3}\tilde{Q}_u^2+\left ( 3\tilde{Q}_2+\tilde{Q}_Q-4\tilde{Q}_u\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
b_{y_t}^{(2)}&=y_t\bigg \{ 54y_t^4+\frac{13}{2}y_b^4+13y_t^2y_b^2+y_b^2y_\tau^2+\lambda^2\left ( \frac{5}{2}\lambda^2+15y_t^2+5y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa \right )\nonumber\\
&{}-\frac{16}{3}g_3^2\left ( \lambda^2+2y_b^2+12y_t^2\right )-6g_2^2\left ( \lambda^2+y_b^2+6y_t^2\right )-g_1^2\left ( \frac{22}{15}\lambda^2+\frac{4}{3}y_b^2+\frac{52}{5}y_t^2\right )\nonumber\\
&{}-2g_1'^2\left [ \lambda^2 \left (\tilde{Q}_1^2+2\tilde{Q}_2^2+\tilde{Q}_S^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )+y_b^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+2\tilde{Q}_Q^2+\tilde{Q}_u^2+\tilde{Q}_d^2\right )\right.\nonumber\\
&{}\left.+12y_t^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2\right )\right ]+\frac{128}{9}g_3^4-\frac{15}{2}g_2^4-\frac{143}{18}g_1^4\nonumber\\
&{}+2g_1'^4\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2\right )\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2-\Sigma_{\tilde{Q}}\right )+16g_3^2g_2^2+\frac{208}{45}g_3^2g_1^2\nonumber\\
&{}+\frac{32}{3}g_3^2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2\right )+\frac{13}{5}g_2^2g_1^2+6g_2^2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\nonumber\\
&{}+\frac{26}{15}g_1^2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\bigg \},\label{eq:USSMYu22Ot2Coeff}

@@

\beta_{a_t}^{(1)}&=a_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\right ]\nonumber\\
&{}+y_t\left [ 2\lambda a_\lambda + 12y_ta_t+2y_ba_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1\right.\nonumber\\
&{}\left.+4g_1'^2M_1'\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\right ],\label{eq:USSMTYu22BetaOneLoop}\\

@@

\beta_{m_{Q3}^2}^{(1)}&=2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+2a_t^2+2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+2a_b^2\nonumber\\
&{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2-\frac{2}{15}g_1^2M_1^2-8\tilde{Q}_Q^2g_1'^2M_1'^2+\frac{1}{5}g_1^2\Sigma_1+2\tilde{Q}_Qg_1'^2\Sigma_1',\label{eq:USSMmq222BetaOneLoop}\\

@@

\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+4a_t^2-\frac{32}{3}g_3^2M_3^2-\frac{32}{15}g_1^1M_1^2-8\tilde{Q}_u^2g_1'^2M_1'^2\nonumber\\
&{}-\frac{4}{5}g_1^2\Sigma_1+2\tilde{Q}_ug_1'^2\Sigma_1',\label{eq:USSMmu222BetaOneLoop}\\
\beta_{m_{u3}^2}^{(2)}&=-32y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )-4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )\nonumber\\
&{}-64y_t^2a_t^2-4\left ( y_ta_b+y_ba_t\right )^2-4\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )\nonumber\\
&{}-4\left ( \lambda a_t + y_ta_\lambda \right )^2+12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )+12g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
&{}-\frac{4}{5}g_1^2y_t^2\left ( -5m_{H_u}^2-m_{Q3}^2+9m_{u3}^2+2M_1^2\right )-\frac{4}{5}g_1^2\left ( a_t^2-2y_ta_tM_1 \right )\nonumber\\
&{}-\frac{8}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2\right )-\frac{8}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
&{}-\frac{8}{5}g_1^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_{Di}^2-m_{\overline{D}i}^2 \right )+\lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2 \right )\right ]\nonumber\\
&{}+8g_1'^2y_t^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2-\tilde{Q}_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
&{}+8g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2-\tilde{Q}_u^2\right )\left ( a_t^2-2y_ta_tM_1'\right )-24\tilde{Q}_ug_1'^2y_t^2\left (\tilde{Q}_2m_{H_u}^2+\tilde{Q}_Qm_{Q3}^2+\tilde{Q}_um_{u3}^2\right )\nonumber\\
&{}-24\tilde{Q}_ug_1'^2y_b^2\left ( \tilde{Q}_1m_{H_d}^2+\tilde{Q}_Qm_{Q3}^2+\tilde{Q}_dm_{d3}^2\right )-8\tilde{Q}_ug_1'^2y_\tau^2\left ( \tilde{Q}_1m_{H_d}^2+\tilde{Q}_Lm_{L3}^2+\tilde{Q}_em_{e3}^2\right )\nonumber\\
&{}-12\tilde{Q}_ug_1'^2\sum_{i=1}^3\kappa_i^2\left ( \tilde{Q}_Sm_S^2+\tilde{Q}_Dm_{Di}^2+\tilde{Q}_{\overline{D}}m_{\overline{D}i}^2\right )\nonumber\\
&{}-8\tilde{Q}_ug_1'^2\sum_{i=1}^3\left ( \tilde{Q}_1m_{H_d}^2+\tilde{Q}_2m_{H_u}^2+\tilde{Q}_Sm_S^2\right )\nonumber\\
&{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( m_{di}^2+m_{Di}^2+m_{\overline{D}i}^2+2m_{Qi}^2+m_{ui}^2\right )\right ]\nonumber\\
&{}+\frac{64}{45}g_3^2g_1^2\left [ 8\left (M_1^2+M_1M_3+M_3^2\right )-3\sum_{i=1}^3\left ( m_{di}^2-m_{Di}^2+m_{\overline{D}i}^2+m_{qi}^2-2m_{ui}^2\right )\right ]\nonumber\\
&{}+\frac{8}{3}\tilde{Q}_ug_3^2g_1'^2\bigg [ 16\tilde{Q}_u\left (M_1'^2+M_1'M_3+M_3^2\right )\nonumber\\
&{}+12\sum_{i=1}^3\left ( \tilde{Q}_dm_{di}^2+\tilde{Q}_Dm_{Di}^2+\tilde{Q}_{\overline{D}}m_{\overline{D}i}^2+2\tilde{Q}_Qm_{Qi}^2+\tilde{Q}_um_{ui}^2\right )\bigg ]\nonumber\\
&{}+\frac{12}{5}g_2^2g_1^2\left [ m_{H'}^2-m_{\overline{H'}}^2+\sum_{i=1}^3\left ( m_{H_i^d}^2-m_{H_i^u}^2+m_{Li}^2-m_{Qi}^2\right )\right ]\nonumber\\
&{}+12\tilde{Q}_ug_2^2g_1'^2\left [ \tilde{Q}_{H'}m_{H'}^2+\tilde{Q}_{\overline{H'}}m_{\overline{H'}}^2+\sum_{i=1}^3\left ( \tilde{Q}_1m_{H_i^d}^2+\tilde{Q}_2m_{H_i^u}^2+\tilde{Q}_Lm_{Li}^2+3\tilde{Q}_Qm_{Qi}^2\right )\right ]\nonumber\\
&{}+\frac{4}{75}g_1^4\bigg [ 1261M_1^2+21m_{H'}^2+3m_{\overline{H'}}^2\nonumber\\
&{}+\sum_{i=1}^3\left ( 4m_{di}^2+12m_{Di}^2+4m_{\overline{D}i}^2-12m_{ei}^2+21m_{H_i^d}^2+3m_{H_i^u}^2+21m_{Li}^2+3m_{Qi}^2+64m_{ui}^2\right )\bigg ]\nonumber\\
&{}+\frac{4}{15}g_1^2g_1'^2\bigg [ -8\tilde{Q}_u\big ( 9\tilde{Q}_d+9\tilde{Q}_{\overline{D}}-9\tilde{Q}_D+9\tilde{Q}_e-9\tilde{Q}_1+9\tilde{Q}_2+3\tilde{Q}_{\overline{H'}}-3\tilde{Q}_{H'}-9\tilde{Q}_L\nonumber\\
&{}+9\tilde{Q}_Q-22\tilde{Q}_u\big )\left ( M_1^2+M_1M_1'+M_1'^2 \right )+12\tilde{Q}_{H'}^2m_{H'}^2-\tilde{Q}_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
&{}+12\sum_{i=1}^3\big ( -\tilde{Q}_d^2m_{di}^2-\tilde{Q}_{\overline{D}}^2m_{\overline{D}i}^2+\tilde{Q}_D^2m_{Di}^2-\tilde{Q}_e^2m_{ei}^2+\tilde{Q}_1^2m_{H_i^d}^2-\tilde{Q}_2^2m_{H_i^u}^2+\tilde{Q}_L^2m_{Li}^2\nonumber\\
&{}-\tilde{Q}_Q^2m_{Qi}^2+\tilde{Q}_u^2m_{ui}^2\big )-15\tilde{Q}_{\overline{H'}}\tilde{Q}_um_{\overline{H'}}^2+33\tilde{Q}_{H'}\tilde{Q}_um_{H'}^2+\tilde{Q}_u\sum_{i=1}^3\big ( -18\tilde{Q}_dm_{di}^2\nonumber\\
&{}-18\tilde{Q}_{\overline{D}}m_{\overline{D}i}^2+30\tilde{Q}_Dm_{Di}^2-6\tilde{Q}_em_{ei}^2+33\tilde{Q}_1m_{H_i^d}^2-15\tilde{Q}_2m_{H_i^u}^2+33\tilde{Q}_Lm_{Li}^2\nonumber\\
&{}-21\tilde{Q}_Qm_{Qi}^2+84\tilde{Q}_um_{ui}^2\big )\bigg ]+8\tilde{Q}_ug_1'^4\bigg [ 3\tilde{Q}_uM_1'^2\big ( 9\tilde{Q}_d^2+9\tilde{Q}_{\overline{D}}^2+9\tilde{Q}_D^2+3\tilde{Q}_e^2+6\tilde{Q}_1^2\nonumber\\
&{}+6\tilde{Q}_2^2+2\tilde{Q}_{\overline{H'}}^2+2\tilde{Q}_{H'}^2+6\tilde{Q}_L^2+18\tilde{Q}_Q^2+3\tilde{Q}_S^2+11\tilde{Q}_u^2 \big )+2\tilde{Q}_{H'}^3m_{H'}^2+2\tilde{Q}_{\overline{H'}}^3m_{\overline{H'}}^2\nonumber\\
&{}+\sum_{i=1}^3\big ( 3\tilde{Q}_d^3m_{di}^2+3\tilde{Q}_{\overline{D}}^3m_{\overline{D}i}^2+3\tilde{Q}_D^3m_{Di}^2+\tilde{Q}_e^3m_{ei}^2+2\tilde{Q}_1^3m_{H_i^d}^2+2\tilde{Q}_2^3m_{H_i^u}^2+2\tilde{Q}_L^3m_{Li}^2\nonumber\\
&{}+6\tilde{Q}_Q^3m_{Qi}^2+\tilde{Q}_S^3m_{Si}^2+3\tilde{Q}_u^3m_{ui}^2\big )+2\tilde{Q}_u\tilde{Q}_{H'}^2m_{H'}^2+2\tilde{Q}_u\tilde{Q}_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
&{}+\tilde{Q}_u\sum_{i=1}^3\big ( 3\tilde{Q}_d^2m_{di}^2+3\tilde{Q}_{\overline{D}}^2m_{\overline{D}i}^2+3\tilde{Q}_D^2m_{Di}^2+\tilde{Q}_e^2m_{ei}^2+2\tilde{Q}_1^2m_{H_i^d}^2+2\tilde{Q}_2^2m_{H_i^u}^2+2\tilde{Q}_L^2m_{Li}^2\nonumber\\
&{}+6\tilde{Q}_Q^2m_{Qi}^2+\tilde{Q}_S^2m_{Si}^2+3\tilde{Q}_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmu222BetaTwoLoop}\\
